Rarefied Null Models

### 2021-03-24 analysis/rarefy_null_models.Rmd
Update for new file structure.

process_nulls <- function(file_path, n){
  data <- read_tsv(file_path, col_types = cols(plot_id = "c")) %>%
    select(year, plot_id, richness = nbsp, everything(), -sing.sp, -starts_with("CWM"), -n) %>%
    group_by(year)

  means <- data %>%
    select(-plot_id, -richness) %>%
    summarise(across(everything(), mean)) %>%
    pivot_longer(cols = -year, names_to = "metric", values_to = "mean")

  sds <- data %>%
    select(-plot_id, -richness) %>%
    summarise(across(everything(), sd)) %>%
    pivot_longer(cols = -year, names_to = "metric", values_to = "sd")

  stats <- left_join(means, sds, by = c("year", "metric")) %>%
    left_join(data %>% select(year, plot_id, richness) %>% distinct(), by = "year") %>%
    mutate(se = sd/sqrt(n),
           lowerCI = mean - qt(0.975, n - 1) * se, 
           upperCI = mean + qt(0.975, n - 1) * se)  %>%
    select(year, plot_id, everything())

@@

plan(multiprocess)
null_table <- future_map_dfr(null_files, process_nulls, n = n)

>>>>

process_nulls <- function(file_path, n){
  data <- read_tsv(file_path) %>%
    rename(richness = nbsp) %>%
    select(-sing.sp) %>%
    group_by(year)

  means <- data %>%
    select(-rarefyid, -richness) %>%
    summarise(across(everything(), mean)) %>%
    pivot_longer(cols = -year, names_to = "metric", values_to = "mean")

  sds <- data %>%
    select(-rarefyid, -richness) %>%
    summarise(across(everything(), sd)) %>%
    pivot_longer(cols = -year, names_to = "metric", values_to = "sd")

  stats <- left_join(means, sds, by = c("year", "metric")) %>%
    left_join(data %>% select(year, rarefyid, rarefy_resamp, richness) %>% distinct(), by = "year") %>%
    mutate(se = sd/sqrt(n),
           lowerCI = mean - qt(0.975, n - 1) * se, 
           upperCI = mean + qt(0.975, n - 1) * se)  %>%
    select(year, rarefyid, everything())

@@

plan(multiprocess)
null_table <- future_map_dfr(null_files, process_nulls, n = 500)
